---
title: "Group 25 CA pollution burden"
author: "Allison Gracer & Mae Rennick"
date: "11/12/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
```


```{r}
# read in the data
ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()
```


## Visualization 

Add a new code chunk to create a basic ggplot2 scatterplot graph (with geom_point) showing % white (x-axis: white_percent, note: depending on your OS this column name might be simplified by janitor::clean_names() to just ‘white’ instead) versus CalEnviroScreen pollution burden score (y-axis: ces_3_0_score). Do not update / finalize the graph further - this is what you will both work on in the next steps. 


```{r}

ggplot(ces, aes( x= white_percent, y= ces_3_0_score)) +
  geom_point() +
  geom_hex() +
  labs(x = "\nPercent of white population (%)\n",
       y = "\nCES 3.0 score\n")


```

