---
title: "Group 25 CA pollution burden"
author: "Allison Gracer & Mae Rennick"
date: "11/12/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#Attach packages
library(tidyverse)
library(janitor)
library(here)
library(hexbin)
```


```{r}
# read in the data
ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()
```


## Data Visualization 

ggplot2 scatterplot graph (with geom_point) showing % white versus CalEnviroScreen pollution burden score 


```{r}
# visualize the data

ggplot(ces, aes( x= white_percent, y= ces_3_0_score)) +
  geom_hex() +
  labs(x = "\nPercent of white population (%)\n",
       y = "\nCES 3.0 score\n")+
  scale_fill_gradient(low = "lightblue", high = "darkblue")+
  theme_minimal()


```

**Figure 1:** Percent white population compared to the CalEnviroScreen 3.0 (CSE) in California. The higher count of the population is indicated by color. 


## Take Aways

Overall, we can extrapolate from this figure that individuals with races other than 'white' are disproportionately affected by multiple sources of pollution, which is represented by the CES 3.0 score. There appears to be a negative correlation between CES 3.0 scores and increasing proportion of white individuals in a community. When percentage of white individuals is lower, we see a high density cluster of CES scores at mid range values (40-60), and at the highest percentage of white individuals in a given population, we see a high density cluster of CES 3.0 scores at low values (0-20), suggesting that at larger percent of white individuals in a population, the less vulnerable the population will be to nearby hazardous environmental conditions. 



## References

U.S. Census Bureau, 2010 Census of Population and Housing, Population and Housing Unit Counts, CPH-2-6, California U.S. Government Printing Office, Washington, DC, 2012.
